Sequential rank agreement methods for comparison of ranked lists

### 2015-08-19 latex/paper.Rnw
homogenizing graphics

<<fig-ao1, echo=FALSE, fig=TRUE,include=FALSE, eval=TRUE>>=
myres <- average_overlap(inputmatrix[,1:2])
myres2 <- average_overlap(inputmatrix[-c(1,2),1:2])
xvals <- 1:500
plot(xvals, myres[xvals], xlim=c(1, 150), ylim=c(0,1), type="l", lwd=2, ylab="Average overlap", xlab="List depth", bty="n")
lines(xvals[-c(1,2)], myres2[1:498], col="red", lwd=2)
@

<<fig-ao2, echo=FALSE, fig=TRUE,include=FALSE, eval=TRUE>>=
mmyres <- sra(inputmatrix[,1:2])
mmyres2 <- sra(inputmatrix[-c(1,2),1:2])
xvals <- 1:500
plot(xvals, mmyres[xvals], xlim=c(1, 150), ylim=c(0, 110), type="l", lwd=2, ylab="Sequential rank agreement", xlab="List depth", bty="n")
lines(xvals[-c(1,2)], mmyres2[1:498], col="red", lwd=2)
@

>>>>

<<fig-ao1, echo=FALSE, fig=TRUE,include=FALSE, eval=TRUE>>=
myres <- average_overlap(inputmatrix[,1:2])
myres2 <- average_overlap(inputmatrix[-c(1,2),1:2])
xvals <- 1:500
plot(xvals, myres[xvals], xlim=c(1, 150), ylim=c(0,1), type="l", lwd=3, ylab="Average overlap", xlab="List depth", bty="n")
lines(xvals[-c(1,2)], myres2[1:498], col="red", lwd=3)
@

<<fig-ao2, echo=FALSE, fig=TRUE,include=FALSE, eval=TRUE>>=
mmyres <- sra(inputmatrix[,1:2])
mmyres2 <- sra(inputmatrix[-c(1,2),1:2])
xvals <- 1:500
plot(xvals, mmyres[xvals], xlim=c(1, 150), ylim=c(0, 110), type="l", lwd=3, ylab="Sequential rank agreement", xlab="List depth", bty="n")
lines(xvals[-c(1,2)], mmyres2[1:498], col="red", lwd=3)
@
